Predictions

### 2021-07-17 analysis/03_laws-repression.Rmd
Remove REWB stuff

  # Load actual model objects
  tar_load(c(m_pts_baseline, m_pts_total, m_pts_total_new, 
             m_pts_advocacy, m_pts_entry, m_pts_funding, 
             m_pts_baseline_rewb, m_pts_total_rewb, 
             m_pts_advocacy_rewb, m_pts_entry_rewb, m_pts_funding_rewb, 
             m_clphy_baseline, m_clphy_total, m_clphy_total_new, 
             m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
             m_clphy_baseline_rewb, m_clphy_total_rewb, 
             m_clphy_advocacy_rewb, m_clphy_entry_rewb, m_clphy_funding_rewb, 
             m_clpriv_baseline, m_clpriv_total, m_clpriv_total_new,
             m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
             m_clpriv_baseline_rewb, m_clpriv_total_rewb, 
             m_clpriv_advocacy_rewb, m_clpriv_entry_rewb, m_clpriv_funding_rewb,
             m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
             m_lhr_advocacy, m_lhr_entry, m_lhr_funding))

  # Load regression tables
  tar_load(c(models_tbl_e1a_re, models_tbl_e1a_rewb, 
             models_tbl_e1b_re, models_tbl_e1c_re, models_tbl_e1d_re))

@@

```{r clean-data}
models <- model_df %>% 
  filter(!str_detect(model, "train")) %>% 
  mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
  mutate(across(c(outcome_var, explan_var, re, family), ~fct_inorder(., ordered = TRUE)))

@@

```{r tbl-e1a-re}
# Build nicer column names
models_for_table_e1a_re <- models %>% 
  filter(outcome_var == "Political terror", re == "RE") %>% 
  mutate(outcome_var = recode(outcome_var, "Political terror" = "PTS"),
         explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))

@@

```{r tbl-e1a-rewb}
models_for_table_e1a_rewb <- models %>% 
  filter(outcome_var == "Political terror", re == "REWB") %>% 
  mutate(outcome_var = recode(outcome_var, "Political terror" = "PTS"),
         explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))

models_names_table_e1a_rewb <- models_for_table_e1a_rewb %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e1a_rewb$model)

names(models_tbl_e1a_rewb) <- recode(names(models_tbl_e1a_rewb), 
                                     !!!models_names_table_e1a_rewb)

modelsummary(models_tbl_e1a_rewb,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

@@

```{r plot-coefs-e1a}
coef_plots <- models %>% 
  filter(str_detect(model, "pts_"), !str_detect(model, "baseline")) %>% 
  mutate(re_fancy = case_when(
    re == "RE" ~ "Random effects models",
    re == "REWB" ~ "Random effects—within/between models"
  )) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  filter(!str_detect(.variable, "between")) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value, fill = re_fancy)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  facet_wrap(vars(re_fancy), ncol = 2, scales = "free_y") +
  theme_ngo()
```

@@

mfx <- models %>% 
  filter(str_detect(model, "_pts"), !str_detect(model, "rewb|baseline")) %>% 
  left_join(plot_pts_vars_lookup, by = "model") %>% 
  mutate(fx = map2(actual_model, plot_var, 
                   ~conditional_effects(.x, effects = .y,
                                        categorical = TRUE)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

@@

```{r tbl-e1b-re}
models_for_table_e1b_re <- models %>% 
  filter(outcome_var == "Physical violence", re == "RE") %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))

@@

```{r plot-coefs-e1b}
coef_plots <- models %>% 
  filter(str_detect(model, "clphy"), !str_detect(model, "baseline")) %>% 
  mutate(re_fancy = case_when(
    re == "RE" ~ "Random effects models",
    re == "REWB" ~ "Random effects—within/between models"
  )) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  filter(!str_detect(.variable, "between")) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value, fill = re_fancy)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  facet_wrap(vars(re_fancy), ncol = 2, scales = "free_y") +
  theme_ngo()
```

@@

mfx <- models %>% 
  filter(str_detect(model, "clphy"), !str_detect(model, "rewb|baseline")) %>% 
  left_join(plot_clphy_vars_lookup, by = "model") %>% 
  mutate(fx = map2(actual_model, plot_var, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

@@

```{r tbl-e1c-re}
models_for_table_e1c_re <- models %>% 
  filter(outcome_var == "Private civil liberties", re == "RE") %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))

@@

```{r plot-coefs-e1c}
coef_plots <- models %>% 
  filter(str_detect(model, "clpriv"), !str_detect(model, "baseline")) %>% 
  mutate(re_fancy = case_when(
    re == "RE" ~ "Random effects models",
    re == "REWB" ~ "Random effects—within/between models"
  )) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  filter(!str_detect(.variable, "between")) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value, fill = re_fancy)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  facet_wrap(vars(re_fancy), ncol = 2, scales = "free_y") +
  theme_ngo()
```

@@

mfx <- models %>% 
  filter(str_detect(model, "clpriv"), !str_detect(model, "rewb|baseline")) %>% 
  left_join(plot_clpriv_vars_lookup, by = "model") %>% 
  mutate(fx = map2(actual_model, plot_var, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

@@

```{r tbl-e1d-re}
models_for_table_e1d_re <- models %>% 
  filter(outcome_var == "Latent human rights", re == "RE") %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))

@@

```{r plot-coefs-e1d}
coef_plots <- models %>% 
  filter(str_detect(model, "lhr"), !str_detect(model, "baseline")) %>% 
  mutate(re_fancy = case_when(
    re == "RE" ~ "Random effects models",
    re == "REWB" ~ "Random effects—within/between models"
  )) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  filter(!str_detect(.variable, "between")) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value, fill = re_fancy)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  facet_wrap(vars(re_fancy), ncol = 2, scales = "free_y") +
  theme_ngo()
```

@@

mfx <- models %>% 
  filter(str_detect(model, "lhr"), !str_detect(model, "rewb|baseline")) %>% 
  left_join(plot_lhr_vars_lookup, by = "model") %>% 
  mutate(fx = map2(actual_model, plot_var, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

>>>>

  # Load actual model objects
  tar_load(c(m_pts_baseline, m_pts_total, m_pts_total_new, 
             m_pts_advocacy, m_pts_entry, m_pts_funding, 
             m_clphy_baseline, m_clphy_total, m_clphy_total_new, 
             m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
             m_clpriv_baseline, m_clpriv_total, m_clpriv_total_new,
             m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
             m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
             m_lhr_advocacy, m_lhr_entry, m_lhr_funding))

  # Load regression tables
  tar_load(c(models_tbl_e1a_re, models_tbl_e1b_re, 
             models_tbl_e1c_re, models_tbl_e1d_re))

@@

```{r clean-data}
models <- model_df %>% 
  filter(!str_detect(model, "train")) %>% 
  mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
  mutate(across(c(outcome_var, explan_var, family), ~fct_inorder(., ordered = TRUE)))

@@

```{r tbl-e1a-re}
# Build nicer column names
models_for_table_e1a_re <- models %>% 
  filter(outcome_var == "Political terror") %>% 
  mutate(outcome_var = recode(outcome_var, "Political terror" = "PTS"),
         explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))

@@

@@

```{r plot-coefs-e1a}
coef_plots <- models %>% 
  filter(str_detect(model, "pts_"), !str_detect(model, "baseline")) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  theme_ngo()
```

@@

mfx <- models %>% 
  filter(str_detect(model, "_pts"), !str_detect(model, "baseline|new")) %>% 
  left_join(plot_pts_vars_lookup, by = "model") %>% 
  mutate(fx = map2(actual_model, plot_var, 
                   ~conditional_effects(.x, effects = .y,
                                        categorical = TRUE)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

@@

```{r tbl-e1b-re}
models_for_table_e1b_re <- models %>% 
  filter(outcome_var == "Physical violence") %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))

@@

```{r plot-coefs-e1b}
coef_plots <- models %>% 
  filter(str_detect(model, "clphy"), !str_detect(model, "baseline")) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  theme_ngo()
```

@@

mfx <- models %>% 
  filter(str_detect(model, "clphy"), !str_detect(model, "new|baseline")) %>% 
  left_join(plot_clphy_vars_lookup, by = "model") %>% 
  mutate(fx = map2(actual_model, plot_var, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

@@

```{r tbl-e1c-re}
models_for_table_e1c_re <- models %>% 
  filter(outcome_var == "Private civil liberties") %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))

@@

```{r plot-coefs-e1c}
coef_plots <- models %>% 
  filter(str_detect(model, "clpriv"), !str_detect(model, "baseline")) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  theme_ngo()
```

@@

mfx <- models %>% 
  filter(str_detect(model, "clpriv"), !str_detect(model, "new|baseline")) %>% 
  left_join(plot_clpriv_vars_lookup, by = "model") %>% 
  mutate(fx = map2(actual_model, plot_var, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

@@

```{r tbl-e1d-re}
models_for_table_e1d_re <- models %>% 
  filter(outcome_var == "Latent human rights") %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))

@@

```{r plot-coefs-e1d}
coef_plots <- models %>% 
  filter(str_detect(model, "lhr"), !str_detect(model, "baseline")) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  theme_ngo()
```

@@

mfx <- models %>% 
  filter(str_detect(model, "lhr"), !str_detect(model, "new|baseline")) %>% 
  left_join(plot_lhr_vars_lookup, by = "model") %>% 
  mutate(fx = map2(actual_model, plot_var, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

### 2021-07-17 analysis/03_model-details.Rmd
Remove REWB stuff

  # So we do it this manual way
  tar_load(c(m_pts_baseline, m_pts_total, m_pts_advocacy, 
             m_pts_entry, m_pts_funding, m_pts_v2csreprss, 
             m_pts_baseline_rewb, m_pts_total_rewb, m_pts_advocacy_rewb, 
             m_pts_entry_rewb, m_pts_funding_rewb, m_pts_v2csreprss_rewb, 
             m_clphy_baseline, m_clphy_total, m_clphy_advocacy, 
             m_clphy_entry, m_clphy_funding, m_clphy_v2csreprss, 
             m_clphy_baseline_rewb, m_clphy_total_rewb, m_clphy_advocacy_rewb, 
             m_clphy_entry_rewb, m_clphy_funding_rewb, m_clphy_v2csreprss_rewb, 
             m_clpriv_baseline, m_clpriv_total, m_clpriv_advocacy, 
             m_clpriv_entry, m_clpriv_funding, m_clpriv_v2csreprss, 
             m_clpriv_baseline_rewb, m_clpriv_total_rewb, m_clpriv_advocacy_rewb, 
             m_clpriv_entry_rewb, m_clpriv_funding_rewb, m_clpriv_v2csreprss_rewb))
})
```

@@

```{r running-time-e1}
models_e1 <- model_df %>% 
  filter(!str_detect(model, "v2csreprss")) %>% 
  mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
  mutate(across(c(outcome_var, explan_var, re, family), ~fct_inorder(., ordered = TRUE)))

model_time_e1 <- models_e1 %>% 
  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
  select(-actual_model) %>% 
  unnest(duration) %>% 
  mutate(model = glue("<code>{model}</code>")) %>% 
  group_by(Model = model, Outcome = outcome_var, `Main predictor` = explan_var, 
           `Random effects` = re, `Family` = family) %>% 
  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
  ungroup() %>% 
  arrange(Outcome, `Main predictor`, `Random effects`)

@@

```{r running-time-e2}
models_e2 <- model_df %>% 
  filter(str_detect(model, "baseline") | str_detect(model, "v2csreprss")) %>% 
  mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
  mutate(across(c(outcome_var, explan_var, re, family), ~fct_inorder(., ordered = TRUE)))

model_time_e2 <- models_e2 %>% 
  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
  select(-actual_model) %>% 
  unnest(duration) %>% 
  mutate(model = glue("<code>{model}</code>")) %>% 
  group_by(Model = model, Outcome = outcome_var, `Main predictor` = explan_var, 
           `Random effects` = re, `Family` = family) %>% 
  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
  ungroup() %>% 
  arrange(Outcome, `Main predictor`, `Random effects`)

>>>>

  # So we do it this manual way
  tar_load(c(m_pts_baseline, m_pts_total, m_pts_total_new, 
             m_pts_advocacy, m_pts_entry, m_pts_funding, 
             m_pts_v2csreprss, 
             m_clphy_baseline, m_clphy_total, m_clphy_total_new, 
             m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
             m_clphy_v2csreprss, 
             m_clpriv_baseline, m_clpriv_total, m_clpriv_total_new, 
             m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
             m_clpriv_v2csreprss, 
             m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
             m_lhr_advocacy, m_lhr_entry, m_lhr_funding, 
             m_lhr_v2csreprss, 
             m_pts_baseline_train, m_pts_total_train, 
             m_pts_advocacy_train, m_pts_entry_train, m_pts_funding_train, 
             m_pts_v2csreprss_train, 
             m_clphy_baseline_train, m_clphy_total_train, 
             m_clphy_advocacy_train, m_clphy_entry_train, m_clphy_funding_train, 
             m_clphy_v2csreprss_train, 
             m_clpriv_baseline_train, m_clpriv_total_train, 
             m_clpriv_advocacy_train, m_clpriv_entry_train, m_clpriv_funding_train, 
             m_clpriv_v2csreprss_train))
})
```

```{r set-computer-details}
computer <- "Work"

if (computer == "Work") {
  computer_details <- "2019 MacBook Pro with 16 cores and 32 GB of RAM, using Stan through brms through cmdstanr"
} else {
  computer_details <- "2016 MacBook Pro with 4 cores and 16 GB of RAM, using Stan through brms through cmdstanr"
}
```

We ran these models on a `r computer_details`.

@@

### Full data

```{r running-time-e1}
models_e1 <- model_df %>% 
  filter(!str_detect(model, "v2csreprss")) %>% 
  mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
  mutate(across(c(outcome_var, explan_var, family), ~fct_inorder(., ordered = TRUE)))

model_time_e1 <- models_e1 %>% 
  filter(training == "Full data") %>% 
  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
  select(-actual_model) %>% 
  unnest(duration) %>% 
  mutate(model = glue("<code>{model}</code>")) %>% 
  group_by(Model = model, Outcome = outcome_var, 
           `Main predictor` = explan_var, `Family` = family) %>% 
  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
  ungroup() %>% 
  arrange(Outcome, `Main predictor`)

### Training data

```{r running-time-e1-training}
model_time_e1 <- models_e1 %>% 
  filter(training == "Training") %>% 
  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
  select(-actual_model) %>% 
  unnest(duration) %>% 
  mutate(model = glue("<code>{model}</code>")) %>% 
  group_by(Model = model, Outcome = outcome_var, 
           `Main predictor` = explan_var, `Family` = family) %>% 
  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
  ungroup() %>% 
  arrange(Outcome, `Main predictor`)

@@

### Full data

```{r running-time-e2}
models_e2 <- model_df %>% 
  filter(str_detect(model, "baseline") | str_detect(model, "v2csreprss")) %>% 
  mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
  mutate(across(c(outcome_var, explan_var, family), ~fct_inorder(., ordered = TRUE)))

model_time_e2 <- models_e2 %>% 
  filter(training == "Full data") %>% 
  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
  select(-actual_model) %>% 
  unnest(duration) %>% 
  mutate(model = glue("<code>{model}</code>")) %>% 
  group_by(Model = model, Outcome = outcome_var, 
           `Main predictor` = explan_var, `Family` = family) %>% 
  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
  ungroup() %>% 
  arrange(Outcome, `Main predictor`)

### Training data

```{r running-time-e2-training}
model_time_e2 <- models_e2 %>% 
  filter(training == "Training") %>% 
  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
  select(-actual_model) %>% 
  unnest(duration) %>% 
  mutate(model = glue("<code>{model}</code>")) %>% 
  group_by(Model = model, Outcome = outcome_var, 
           `Main predictor` = explan_var, `Family` = family) %>% 
  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
  ungroup() %>% 
  arrange(Outcome, `Main predictor`)

### 2021-07-17 analysis/03_modeling-choices.Rmd
Remove REWB stuff

  canary <- tar_read(panel_lagged)
})

# canary <- canary %>%
#   mutate(gwcode = as.factor(gwcode), year = as.factor(year)) %>%  # Make a factor
#   mutate(PTS_factor_lead1 = ordered(PTS_factor_lead1)) %>%  # Make this ordered
#   # To do fancy Bell and Jones adjustment (https://doi.org/10.1017/psrm.2014.7)
#   # (aka Mundlak devices), explanatory variables should be split into a meaned
#   # version (\bar{x}) and a de-meaned version (x - \bar{x}) so that they can
#   # explain the within-group and between-group variation. We de-mean three variables here:
#   group_by(gwcode) %>%
#   mutate_at(vars(v2csreprss, v2x_polyarchy, gdpcap_log),
#             list(between = ~mean(., na.rm = TRUE),  # Between, for countries
#                  within = ~. - mean(., na.rm = TRUE))) %>%   # Within, for countries
#   ungroup()
```

@@

>>>>

  canary <- tar_read(panel_lagged)
})
```

@@

BUT for the sake of computational efficiency, we omit the within/between split. It takes 30-120 minutes to run one within/between model, and running dozens can take all day. The predictive results are nearly identical to models without the split, and since we're more interested in prediction than in individual coefficient effects, we don't need to wait hours for the same results we'd get with the original non-demeaned values.

### 2021-07-17 analysis/04_predictions.Rmd
Remove REWB stuff

  # Load actual model objects
  tar_load(c(m_pts_baseline_train, m_pts_v2csreprss_train,
             m_pts_total_train, m_pts_advocacy_train, 
             m_pts_entry_train, m_pts_funding_train,
             m_pts_baseline_rewb_train, m_pts_v2csreprss_rewb_train, 
             m_clphy_baseline_train, m_clphy_v2csreprss_train, 
             m_clphy_total_train, m_clphy_advocacy_train, 
             m_clphy_entry_train, m_clphy_funding_train,
             m_clpriv_baseline_train, m_clpriv_v2csreprss_train,
             m_clpriv_total_train, m_clpriv_advocacy_train, 
             m_clpriv_entry_train, m_clpriv_funding_train,
             m_lhr_baseline_train, m_lhr_v2csreprss_train,
             m_lhr_total_train, m_lhr_advocacy_train, 
             m_lhr_entry_train, m_lhr_funding_train))
})

@@

set.seed(seed_pts_prediction)
pred_pts_v2csreprss <- predict(
  m_pts_v2csreprss_train, 
  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
  allow_new_levels = TRUE
) %>% 
  as_tibble() %>% 
  magrittr::set_colnames(pts_levels)

set.seed(seed_pts_prediction)
pred_pts_baseline_rewb <- predict(
  m_pts_baseline_rewb_train, 
  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
  allow_new_levels = TRUE
) %>% 
  as_tibble() %>% 
  magrittr::set_colnames(pts_levels)

set.seed(seed_pts_prediction)
pred_pts_v2csreprss_rewb <- predict(
  m_pts_v2csreprss_rewb_train, 
  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
  allow_new_levels = TRUE
) %>% 
  as_tibble() %>% 
  magrittr::set_colnames(pts_levels)
```

@@

### Baseline model (REWB)

```{r e2a-separation-baseline-rewb}
# Match each column in pred_mat (predicted probabilities for each response level)
pred_long_list <- lapply(1:ncol(pred_pts_baseline_rewb), 
                         FUN = match_actual, 
                         pred = pred_pts_baseline_rewb, 
                         actual = as.character(canary_testing_lagged$PTS_factor_lead1))

n_in_group <- nrow(pred_pts_baseline_rewb)

### Model with civil society repression (REWB)

```{r e2a-separation-cs-rewb}
pred_long_list <- lapply(1:ncol(pred_pts_v2csreprss_rewb), 
                         FUN = match_actual, 
                         pred = pred_pts_v2csreprss_rewb, 
                         actual = as.character(canary_testing_lagged$PTS_factor_lead1))

n_in_group <- nrow(pred_pts_v2csreprss_rewb)

@@

pred_pts_baseline_categories_rewb <- pred_pts_baseline_rewb %>% 
  rownames_to_column() %>% 
  pivot_longer(-rowname) %>% 
  group_by(rowname) %>% 
  filter(rank(-value, ties.method = "last") == 1) %>% 
  ungroup() %>% 
  select(predicted = name)

pred_pts_v2csreprss_categories_rewb <- pred_pts_v2csreprss_rewb %>% 
  rownames_to_column() %>% 
  pivot_longer(-rowname) %>% 
  group_by(rowname) %>% 
  filter(rank(-value, ties.method = "last") == 1) %>% 
  ungroup() %>% 
  select(predicted = name)

@@

pts_cat_preds_rewb <- canary_testing_lagged %>% 
  select(country, year, actual = PTS_factor_lead1) %>% 
  mutate(pred_baseline = pred_pts_baseline_categories_rewb$predicted,
         pred_v2csreprss = pred_pts_v2csreprss_categories_rewb$predicted) %>% 
  filter(!is.na(actual)) %>%
  mutate(is_correct_baseline = actual == pred_baseline,
         is_correct_v2csreprss = actual == pred_v2csreprss)

@@

pts_improved_rewb <- pts_cat_preds_rewb %>% 
  filter(!is_correct_baseline & is_correct_v2csreprss) %>% 
  select(Country = country, Year = year, Actual = actual,
         `CS repression included` = pred_v2csreprss,
         `Baseline` = pred_baseline)

@@

pts_pred_table_rewb <- pts_cat_preds_rewb %>% 
  pivot_longer(starts_with("is_correct")) %>% 
  group_by(name, value) %>% 
  summarize(n = n()) %>% 
  ungroup() %>% 
  left_join(correct_lookup, by = "name") %>% 
  mutate(Prediction = ifelse(value == TRUE, "Correct", "Wrong")) %>% 
  arrange(nice_name) %>% 
  select(-name, -value) %>% 
  pivot_wider(names_from = "nice_name", values_from = "n")

pts_pred_table %>% 
  kbl(align = "lcc") %>% 
  kable_styling()

pts_pred_table_rewb %>% 
  kbl(align = "lcc") %>% 
  kable_styling()
```

>>>>

  # Load actual model objects
  tar_load(c(m_pts_baseline_train, m_pts_v2csreprss_train,
             m_pts_total_train, m_pts_advocacy_train, 
             m_pts_entry_train, m_pts_funding_train,
             m_clphy_baseline_train, m_clphy_v2csreprss_train, 
             m_clphy_total_train, m_clphy_advocacy_train, 
             m_clphy_entry_train, m_clphy_funding_train,
             m_clpriv_baseline_train, m_clpriv_v2csreprss_train,
             m_clpriv_total_train, m_clpriv_advocacy_train, 
             m_clpriv_entry_train, m_clpriv_funding_train,
             m_lhr_baseline_train, m_lhr_v2csreprss_train,
             m_lhr_total_train, m_lhr_advocacy_train, 
             m_lhr_entry_train, m_lhr_funding_train))
})

@@

set.seed(seed_pts_prediction)
pred_pts_v2csreprss <- predict(
  m_pts_v2csreprss_train, 
  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
  allow_new_levels = TRUE
) %>% 
  as_tibble() %>% 
  magrittr::set_colnames(pts_levels)
```

@@

@@

@@

@@

@@

pts_pred_table %>% 
  kbl(align = "lcc") %>% 
  kable_styling()
```
